### 2016-02-13 mcmc.tex
Switch from 'endnotes' package to 'enotez'.

\documentclass[12pt,twoside,pdftex]{article}
\usepackage{styles/dar_endnotes}

@@

@@

One thing we can keep in mind to guide us in this is what we said above (\sectionname~\ref{sec:sampling}),
  which is that samplings are good for doing \emph{integrals}.
We should endeavor to use as our ``results'' outputs from the \MCMC\ 
  that are based on integrals computed with the sampling.
This includes expectations, medians, quantiles, one-dimensional histograms,
  and multi-dimensional histograms.
This does \emph{not} include the ``best'' sample or a mode or optimum.
The latter things are not necessarily illegitimate outputs of the \MCMC,
  but they do not make best use of the fact that the sampling is a tool for integration,
  and we do not recommend them.

@@

\clearpage
\markright{Notes}\theendnotes

>>>>

\documentclass[12pt,twoside,pdftex]{article}
\usepackage[backref=true]{enotez}

@@

\let\note=\endnote

\DeclareInstance{enotez-list}{custom}{paragraph}
{
  number = \makebox[0pt][r]{\textsuperscript{#1}},
  format = \indent\normalfont,
  number-format = \bfseries,
}

@@

One thing we can keep in mind to guide us in this is what we said above (\sectionname{sec:sampling}),
  which is that samplings are good for doing \emph{integrals}.
We should endeavor to use as our ``results'' outputs from the \MCMC\ 
  that are based on integrals computed with the sampling.
This includes expectations, medians, quantiles, one-dimensional histograms,
  and multi-dimensional histograms.
This does \emph{not} include the ``best'' sample or a mode or optimum.
The latter things are not necessarily illegitimate outputs of the \MCMC,
  but they do not make best use of the fact that the sampling is a tool for integration,
  and we do not recommend them.

@@

\clearpage
\markright{Notes}\printendnotes[custom]
